Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-25 paper.qmd
MNIST removed model points from the trimesh

trimesh_removed_mnist <- vis_rmlg_mesh(
  distance_edges = distance_mnist, 
  benchmark_value = benchmark_mnist, 
  tr_coord_df = tr_from_to_df_mnist, 
  distance_col = "distance") +
  geom_point(data = pacmap_minst_scaled,
             aes(
               x = PaCMAP1,
               y = PaCMAP2
             ),
             alpha=0.5, 
             size = 0.1) +
  interior_annotation("a", sc_ltr_pos_mnist)

>>>>

tr_df <- distinct(tibble::tibble(
  x = c(tr_from_to_df_mnist[["x_from"]], tr_from_to_df_mnist[["x_to"]]), 
  y = c(tr_from_to_df_mnist[["y_from"]], tr_from_to_df_mnist[["y_to"]])))

distance_df_small_edges_mnist <- distance_mnist |>
  filter(distance < benchmark_mnist)

tr_from_to_df_mnist <- inner_join(
  tr_from_to_df_mnist, distance_df_small_edges_mnist, 
  by = c("from", "to"))

trimesh_removed_mnist <- ggplot() + 
  geom_segment(data = tr_from_to_df_mnist, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#33a02c") +
  geom_point(data = pacmap_minst_scaled,
             aes(
               x = PaCMAP1,
               y = PaCMAP2
             ),
             alpha=0.5, 
             size = 0.1) +
  interior_annotation("a", sc_ltr_pos_mnist)

# trimesh_removed_mnist <- vis_rmlg_mesh(
#   distance_edges = distance_mnist, 
#   benchmark_value = benchmark_mnist, 
#   tr_coord_df = tr_from_to_df_mnist, 
#   distance_col = "distance") +
#   geom_point(data = pacmap_minst_scaled,
#              aes(
#                x = PaCMAP1,
#                y = PaCMAP2
#              ),
#              alpha=0.5, 
#              size = 0.1) +
#   interior_annotation("a", sc_ltr_pos_mnist)
